Computer Science House Constitution

### 2022-02-14 constitution.tex
Reword and Styling

@@

	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. This will be treated as a House Meeting, with the expectation that all Active Members will attend and attendance will be taken. If the speeches take place at a traditional House Meeting, only one attendance will be taken.

>>>>

\asubsection{Overriding Directorships Qualifications}
When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in \ref{Qualifications}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.

@@
